MetaData262: Computing and Visualizing Test262 MetaData

### 2022-05-30 paper.tex
small fix

% Para 3 --> Trade off the fazer a filtragem local or no servidor
Figure \ref{fig:website} two approaches to the search functionality: server-side search (\emph{Backend Search}) and client-side search (\emph{Local Search}). We provide both approaches because each has its trade offs. The following results were achieved using the laptop that was serving the web application. The server-side search starts slowing down whenever the amount of tests being returned surpasses 2500, taking roughly half a second to get the results. Whereas, the client-search takes around 4 seconds to load all the metadata from the server at page load but is able to filter any query within a few milliseconds. We believe the client-side search to be the most appropriate since is only needs the initial load time. In addition to that, the user can fill in the filters for the search while the data is loading. To further improve this issue, we will be caching the metadata in the users browser this way the metadata would be loaded once.

>>>>

% Para 3 --> Trade off the fazer a filtragem local or no servidor
Figure \ref{fig:website} shows two approaches to the search functionality: server-side search (\emph{Backend Search}) and client-side search (\emph{Local Search}). We provide both approaches because each has its trade offs. The following results were achieved using the laptop that was serving the web application. The server-side search starts slowing down whenever the amount of tests being returned surpasses 2500, taking roughly half a second to get the results. Whereas, the client-search takes around 4 seconds to load all the metadata from the server at page load but is able to filter any query within a few milliseconds. We believe the client-side search to be the most appropriate since is only needs the initial load time. In addition to that, the user can fill in the filters for the search while the data is loading. To further improve this issue, we will be caching the metadata in the users browser this way the metadata would only be loaded once.
